---
title: "bill_thermal_code_1"
author: "Rosalee Elting"
date: "2/23/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Document Working directory for your computer and produce session info into About. **
*Both can now be found in my environment for future reference*
```{r}
About<- sessionInfo()
WD <- getwd()
```

**LOAD LIBRARIES** 
```{r load libraries}
library(Thermimage)
library(ggplot2)
library(tidyr)
library(Thermimage)
library(fields)
```

**EXIFTOOLS NOTE**
*To use this Thermal Package, you will also have to download ExifTools here: https://exiftool.org/install.htm. Also you need to know where it is. The code is written that it is titled "exiftools" with NO extension (such as .exe) and located in the Windows folder (C:/)*

BEGINNING OF CODE, NEED TO MAKE INTO A LOOP EVENTUALLY 


```{r}
for (i in vector) {
  
}
images <- list.files(path="/Users/Mellisuga/Documents/R/bill_thermal_input", pattern="*.jpg")
setwd("/Users/MD/Desktop/Files")
for (j in 1:length(files)){
  i <- read.table(files[j])
  i_automean <- mean(i[1:5651,10])
  i_xmean <- mean(i[5652:7977,10])
  barplot(i[,10]/i_automean, ylim = c(0,2.5))
  abline(h=1, col ="red", lwd =3)
  abline(h=22.06126/i_automean, col ="red", lwd =3)
  abline(v=2300*1.2, col="blue", lwd =3)
  abline(v=5651*1.2, col="blue", lwd=3)
  pdf(paste0(files[j],".pdf"))
  graphics.off()
} 
```


```{r load my image}
#f<-paste0(system.file())
f <-"IR_1913.jpg"
img<-readflirJPG(f, exiftoolpath="C:/")
dim(img)

```

```{r extract metatags from thermal image file}
cams<-flirsettings(f, exiftoolpath="C:/", camvals="")
head(cbind(cams$Info), 20)
```

```{r to see camera calibration constants}
plancks<-flirsettings(f, exiftoolpath="C:/", camvals="-*Planck*")
unlist(plancks$Info)
```

```{r to see file data information}
cbind(unlist(cams$Dates))
```

**Run the following variables to assign the variables from the cams data**
```{r other variables we can add}
ObjectEmissivity<-  cams$Info$Emissivity              # Image Saved Emissivity - should be ~0.95 or 0.96
dateOriginal<-cams$Dates$DateTimeOriginal             # Original date/time extracted from file
dateModif<-   cams$Dates$FileModificationDateTime     # Modification date/time extracted from file
PlanckR1<-    cams$Info$PlanckR1                      # Planck R1 constant for camera  
PlanckB<-     cams$Info$PlanckB                       # Planck B constant for camera  
PlanckF<-     cams$Info$PlanckF                       # Planck F constant for camera
PlanckO<-     cams$Info$PlanckO                       # Planck O constant for camera
PlanckR2<-    cams$Info$PlanckR2                      # Planck R2 constant for camera
ATA1<-        cams$Info$AtmosphericTransAlpha1        # Atmospheric Transmittance Alpha 1
ATA2<-        cams$Info$AtmosphericTransAlpha2        # Atmospheric Transmittance Alpha 2
ATB1<-        cams$Info$AtmosphericTransBeta1         # Atmospheric Transmittance Beta 1
ATB2<-        cams$Info$AtmosphericTransBeta2         # Atmospheric Transmittance Beta 2
ATX<-         cams$Info$AtmosphericTransX             # Atmospheric Transmittance X
OD<-          cams$Info$ObjectDistance                # object distance in metres
FD<-          cams$Info$FocusDistance                 # focus distance in metres
ReflT<-       cams$Info$ReflectedApparentTemperature  # Reflected apparent temperature
AtmosT<-      cams$Info$AtmosphericTemperature        # Atmospheric temperature
IRWinT<-      cams$Info$IRWindowTemperature           # IR Window Temperature
IRWinTran<-   cams$Info$IRWindowTransmission          # IR Window transparency
RH<-          cams$Info$RelativeHumidity              # Relative Humidity
h<-           cams$Info$RawThermalImageHeight         # sensor height (i.e. image height)
w<-           cams$Info$RawThermalImageWidth          # sensor width (i.e. image width)

```


Converting Raw binary to thermal data
If stored with a TIFF header, the data load in as a pre-allocated matrix of the same dimensions of the thermal image, but the values are integers values, in this case ~18000. The data are stored as in binary/raw format at 2^16 bits of resolution = 65536 possible values, starting at 0. These are not temperature values. They are, in fact, radiance values or absorbed infrared energy values in arbitrary units. That is what the calibration constants are for. The conversion to temperature is a complicated algorithm, incorporating Plank’s law and the Stephan Boltzmann relationship, as well as atmospheric absorption, camera IR absorption, emissivity and distance to namea few. Each of these raw/binary values can be converted to temperature, using the raw2temp function:

```{r look at values of data}
str(img)
```
Can add many parameters in Raw2Temp, need to look into that. Looks like with sample data, just the plain Raw2Temp command brings up correct values to within 0.1 degress. 
```{r convert to temperature data}
temperature<-raw2temp(img, E=cams$Info$Emissivity, OD = cams$Info$ObjectDistance, RTemp=cams$Info$ReflectedApparentTemperature, ATemp = cams$Info$AtmosphericTemperature, IRWTemp = cams$Info$IRWindowTemperature, IRT = cams$Info$IRWindowTransmission, RH= cams$Info$RelativeHumidity     )
str(temperature) 
temperature <-raw2temp(img)

temperature<-raw2temp(img, ObjectEmissivity, OD, ReflT, AtmosT, IRWinT, IRWinTran, RH,
                      PlanckR1, PlanckB, PlanckF, PlanckO, PlanckR2, 
                      ATA1, ATA2, ATB1, ATB2, ATX)
str(temperature)      
```
Will need to change height and width of following code for image. Get from flirsettings command (xresolution, yresolution)
```{r plot the temperature data}
library(fields) 
plotTherm(temperature, h=h, w=w, minrangeset=21, maxrangeset=32)

#if rotated, can manipulate with the trans= argument in plotTherm
#plotTherm(temperature, w=72, h=72, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix")

```
Other palette options
```{r palettes}
plotTherm(temperature, w=w, h=h, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix", 
          thermal.palette=rainbowpal)
plotTherm(temperature, w=w, h=h, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix", 
          thermal.palette=glowbowpal)
plotTherm(temperature, w=w, h=h, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix", 
          thermal.palette=midgreypal)
plotTherm(temperature, w=w, h=h, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix", 
          thermal.palette=midgreenpal)
plotTherm(temperature, w=w, h=h, minrangeset = 21, maxrangeset = 32, trans="rotate270.matrix", 
          thermal.palette=rainbow1234pal)
#there are many more
```


Deconvolute temperature to raw and back to temperature: 
With thermal imaging analysis, there are at least 7 environmental parameters that must be known to convert raw to temperature. Sometimes, the parameters might have been incorrectly input by the user or changing the parameters is too cumbersome in the commercial software. temp2raw() is the inverse of raw2temp(), which allows you to convert an estimated temperature back to the raw values (i.e. deconvolute), using the initial object parameters used.
```{r}
#For example, convert a temperature estimated at 23 degrees C, under the default blackbody conditions:
temp2raw(23, E=1, OD=0, RTemp=20, ATemp=20, IRWTemp=20, IRT=1, RH=50, PR1=21106.77, PB=1501, PF=1, PO=-7340, PR2=0.012545258)
```

Which yields a raw value of 17994.06 (using the calibration constants above). Now you can use raw2temp to calculate a better estimate of an object that has emissivity=0.95, distance=1m, window transmission=0.96, all temperatures=20C, 50 RH
Note: the default calibration constants for my FLIR camera will be used if you leave out the calibration data during this two step process, but it is more appropriate to look up your camera’s calibrations constants using the flirsettings() function.

```{r}
raw2temp(17994.06, E=0.95, OD=1, RTemp=20, ATemp=20, IRWTemp=20, IRT=0.96, RH=50, PR1=21106.77, PB=1501, PF=1, PO=-7340, PR2=0.012545258)
```
Finding a way to quantitatively analyse thermal images in R is a challenge due to limited interactions with the graphics environment. Thermimage has a function that allows you to write the image data to a file format that can be easily imported into ImageJ.

First, the image matrix needs to be transposed (t) to swap the row vs. column order in which the data are stored, then the temperatures need to be transformed to a vector, a requirement of the writeBin function. The function writeFlirBin is a wrapper for writeBin, and uses information on image width, height, frame number and image interval (the latter two are included for thermal video saves) **but are kept for simplicity to contruct a filename that incorporates image information required when importing to ImageJ:**

```{r}
knitr::opts_knit$set(root.dir = '/output')
```

```{r}
setwd("C:/Users/Mellisuga/Documents/R/bill_thermal/output")
writeFlirBin(as.vector(t(temperature)), templookup=NULL, w=w, h=h, I="", rootname=cams$Info$FileName)
```



See this link: https://github.com/gtatters/Thermimage#import-raw-file-into-imagej
For converting to Image J, processing a video, or bulk processing many photos for ImageJ analysis. 

